### 2022-03-12 src/text/3-applications-subsections/1D-analysis.tex
Fix pre commit hooks
Add some draft text for the 1D analysis example

\subsection{Classical spectral analysis}
\label{ssec:1D-analysis}
\todo{Axel}
A classical spectral analysis using Reflected Regions. Showing flux points, reflected regions on the CTA galactic center data

\begin{figure*}[t]
	\centering
	\includegraphics[width=1.\textwidth]{figures/cta_galactic_center.pdf}
	\caption{CTA Galactic Center example}
	\label{fig:cta_galactic_center}
\end{figure*}

>>>>

\subsection{1D Analysis}
\label{ssec:1d-analysis}
\todo{Axel}
One of the most common analysis cases in gamma-ray astronomy is measuring the
spectrum of a source in a given region defined on the sky, in conventional
astronomy also called aperture photometry.
The spectrum is typically measured in two steps: first a parametric
spectral model is fitted to the data and secondly flux points are computed
in a pre-defined set of energy bins.
The result of such an analysis performed on three simulated CTA observations
is shown in Fig.~\ref{fig:cta_galactic_center}.
In this case the spectrum was measured in a circular aperture centered
on the Galactic Center, in \gammaray~astronomy often called "on region".
For such analysis the users first chooses a region of interest
and energy binning, both defined by a `RegionGeom`.
In a second step the events and instrument response are binned into
maps of this geometry, by the `SpectrumDatasetMaker`.
All the data and reduced instrument response are bundled into a
`SpectrumDataset`.
To estimate the expected background in the on region a "reflected regions"
background method was used~\cite{Berge07}, represented in \gammapy
by the `ReflectedRegionsBackgroundMaker` class.
The resulting reflected regions are illustrated for all three observations
on top of the map of counts.
After reduction of the data it was modelled using a forward-folding
method and a power-law spectral shape, using the `PowerLawSpectralModel`
and `Fit` class.
Based on this best fit model the final flux points and
corresponding log-likleihood profiles are computed using
the `FluxPointsEstimator`.

\begin{figure*}[t]
	\centering
	\includegraphics[width=1.\textwidth]{figures/cta_galactic_center.pdf}
	\caption{
        Example spectral analysis of the Galactic Center for three simulated CTA observations.
        The left image shows the maps of counts with the measurement region and background
        regions overlaid in different colors. The right image shows the resulting spectral
        points and their corresponding log-likelihood profiles.
    }
	\label{fig:cta_galactic_center}
\end{figure*}
